Parallel Solving of Multiple Information-Coordinated Global Optimization Problems

### 2021-03-08 2020/JPDC_MCO/2020_JPDC.tex
1

In the framework of the proposed approach, the GSA algorithm described above will be used to solve global optimization problems of the set $F$. Moreover, due to the informational connectivity (\ref{eq:5}) of the problems of the set $F$, the search information $A_k$ can be quickly transformed to the values of the next function to be minimized $f(y)$ of the set $F$ and GSA can minimize each successive function $f(y)$, taking into account the results of all previous calculations. The GSA algorithm for solving GO problems of the set $F$ and using search information $A_k$, will be referred to as the \textit{Multiple Global Search Algorithm} (MGSA).

@@

\biboptions{sort&compress}
\bibliography{mybibfile}

>>>>

In the framework of the proposed approach, the GSA algorithm described above will be used to solve global optimization problems of the set $F$. Moreover, due to the informational connectivity (\ref{eq:5}) of the problems of the set $F$, the search information $A_k$ can be quickly transformed to the values of the next function to be minimized $f(y)$ of the set $F$ and GSA can minimize each successive function $f(y)$, taking into account the results of all previous calculations. The GSA algorithm for solving GO problems of the set $F$ and using search information $A_k$, will be referred to as the Multiple Global Search Algorithm (MGSA).

@@

\begin{thebibliography}{10}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\expandafter\ifx\csname href\endcsname\relax
  \def\href#1#2{#2} \def\path#1{#1}\fi

\bibitem{c1}
R.~Arora, Optimization: Algorithms and Applications, CRC Press, 2015.

\bibitem{c2}
M.~Locatelli, F.~Schoen, Global Optimization: Theory, Algorithms, and
  Applications, SIAM, 2013.

\bibitem{c3}
R.~Paulavi{\v c}ius, J.~{\v Z}ilinskas, Simplicial Global Optimization,
  Springer Briefs in Optimization, Springer-Verlag, New-York, 2014.

\bibitem{c4}
X.-S. Yang, Nature-inspired metaheuristic algorithms, Luniver Press, Frome,
  2008.

\bibitem{c5}
A.~Zhigljavsky, A.~{\v Z}ilinskas, Stochastic Global Optimization, Springer,
  2008.

\bibitem{c6}
R.~Strongin, Y.~Sergeyev, Global optimization with non-convex constraints.
  Sequential and parallel algorithms, Kluwer Academic Publishers, Dordrecht,
  2000 (2nd ed. 2013, 3rd ed. 2014).

\bibitem{c7}
Y.~Sergeyev, D.~Kvasov, Deterministic Global Optimization: An Introduction to
  the Diagonal Approach, Springer Briefs in Optimization, Springer-Verlag,
  New-York, 2017.

\bibitem{c8}
L.~M. Rios, N.~V. Sahinidis, Derivative-free optimization: a review of
  algorithms and comparison of software implementations, Journal of Global
  Optimization 56 (2013) 1247--1293.
\newblock \href {https://doi.org/10.1007/s10898-012-9951-y}
  {\path{doi:10.1007/s10898-012-9951-y}}.

\bibitem{c9}
C.~Floudas, C.~Gounaris, A review of recent advances in global optimization,
  Journal of Global Optimization 45~(3) (2009).
\newblock \href {https://doi.org/10.1007/s10898-008-9332-8}
  {\path{doi:10.1007/s10898-008-9332-8}}.

\bibitem{c10}
R.~Mart{\'i}, Multi-Start Methods, Springer, US, Boston, MA, 2003.
\newblock \href {https://doi.org/10.1007/0-306-48056-5_12}
  {\path{doi:10.1007/0-306-48056-5_12}}.

\bibitem{c11}
T.~Krityakierne, C.~Shoemaker, {SOMS}: {SurrOgate} {MultiStart} algorithm for
  use with nonlinear programming for global optimization, International
  transactions in operational research 24~(5) (2017) 1139--1172.

\bibitem{c12}
A.~{\v{Z}}ilinskas, J.~Gillard, M.~Scammell, A.~Zhigljavsky, Multistart with
  early termination of descents, Journal of Global Optimization 79~(2) (2021)
  447--462.
\newblock \href {https://doi.org/10.1007/s10898-019-00814-w}
  {\path{doi:10.1007/s10898-019-00814-w}}.

\bibitem{c13}
Y.~Gao, W.~Du, G.~Yan, Selectively-informed particle swarm optimization,
  Scientific Reports 5~(1) (2015) 92--95.
\newblock \href {https://doi.org/10.1038/srep09295}
  {\path{doi:10.1038/srep09295}}.

\bibitem{c14}
A.~Eiben, J.~Smith, Introduction to evolutionary computing, Springer, Berlin,
  Heidelberg, 2015.

\bibitem{c15}
M.~Gendreau, Handbook of metaheuristics, Springer, New-York, 2010.

\bibitem{c16}
H.~Tuy, Convex Analysis and Global Optimization, Springer, 2016.

\bibitem{c17}
H.~A. Le~Thi, T.~Pham Dinh, {DC} programming and {DCA}: thirty years of
  developments, Mathematical Programming 169~(1) (2018) 5--68.
\newblock \href {https://doi.org/10.1007/s10107-018-1235-y}
  {\path{doi:10.1007/s10107-018-1235-y}}.

\bibitem{c18}
E.~Hansen, G.~Walster, Global optimization using interval analysis: revised and
  expanded, CRC Press, Boca Raton, 2003.

\bibitem{c19}
Y.~Evtushenko, M.~Posypkin, A deterministic approach to global box-constrained
  optimization, Optimization Letters 7~(4) (2013) 819--829.
\newblock \href {https://doi.org/10.1007/s11590-012-0452-1}
  {\path{doi:10.1007/s11590-012-0452-1}}.

\bibitem{c20}
R.~Paulavi{\v{c}}ius, J.~{\v{Z}}ilinskas, A.~Grothey, Parallel branch and bound
  for global optimization with combination of {Lipschitz} bounds, Optimization
  Methods and Software 26~(3) (2011) 487--498.
\newblock \href {https://doi.org/10.1080/10556788.2010.551537}
  {\path{doi:10.1080/10556788.2010.551537}}.

\bibitem{c21}
A.~Gimbutas, A.~{\v{Z}}ilinskas, An algorithm of simplicial {Lipschitz}
  optimization with the bi-criteria selection of simplices for the bi-section,
  Journal of Global Optimization 71~(1) (2018) 115--127.
\newblock \href {https://doi.org/10.1007/s10898-017-0550-9}
  {\path{doi:10.1007/s10898-017-0550-9}}.

\bibitem{c22}
D.~R. Jones, J.~R. R.~A. Martins, The {DIRECT} algorithm: 25 years later,
  Journal of Global Optimization 79~(3) (2021) 521--566.
\newblock \href {https://doi.org/10.1007/s10898-020-00952-6}
  {\path{doi:10.1007/s10898-020-00952-6}}.

\bibitem{c23}
Y.~Sergeyev, R.~Strongin, D.~Lera, Introduction to global optimization
  exploiting space-filling curves, Springer Briefs in Optimization, Springer,
  New-York, 2013.

\bibitem{c25}
R.~Rockafellar, Lipschitzian properties of multifunctions, Nonlinear Analysis:
  Theory, Methods {\&} Applications 9~(8) (1985) 867--885.

\bibitem{c26}
D.~S. Kim, G.~M. Lee, P.~H. Sach, Hartley proper efficiency in multifunction
  optimization, Journal of Optimization Theory and Applications 120~(1) (2004)
  129--145.
\newblock \href {https://doi.org/10.1023/B:JOTA.0000012736.02360.58}
  {\path{doi:10.1023/B:JOTA.0000012736.02360.58}}.

\bibitem{c27}
V.~Gergel, E.~Kozinov, Accelerating parallel multicriterial optimization
  methods based on intensive using of search information, Procedia Computer
  Science 108 (2017) 1463--1472, {International} Conference on Computational
  Science, {ICCS} 2017, 12-14 June 2017, Zurich, Switzerland.
\newblock \href {https://doi.org/10.1016/j.procs.2017.05.051}
  {\path{doi:10.1016/j.procs.2017.05.051}}.

\bibitem{c28}
V.~Gergel, E.~Kozinov, Efficient multicriterial optimization based on intensive
  reuse of search information, J. Glob. Optim. 71~(1) (2018) 73--90.
\newblock \href {https://doi.org/10.1007/s10898-018-0624-3}
  {\path{doi:10.1007/s10898-018-0624-3}}.

\bibitem{c29}
P.~Pardalos, A.~Zilinskas, J.~{\v{Z}}ilinskas, Non-Convex Multi-Objective
  Optimization, Springer Optimization and Its Applications, Springer, 2017.
\newblock \href {https://doi.org/10.1007/978-3-319-61007-8}
  {\path{doi:10.1007/978-3-319-61007-8}}.

\bibitem{c30}
Y.~Collette, P.~Siarry, Multiobjective Optimization: Principles and Case
  Studies (Decision Engineering), Springer-Verlag, Berlin, Heidelberg, 2011.

\bibitem{c31}
E.~Zavadskas, Z.~Turskis, S.~Kildiene, State of art surveys of overviews on
  {MCDM}/{MADM} methods, Technological and Economic Development of Economy 20
  (2014) 165--179.
\newblock \href {https://doi.org/10.3846/20294913.2014.892037}
  {\path{doi:10.3846/20294913.2014.892037}}.

\bibitem{c32}
C.~Hillermeier, J.~Jahn, Multiobjective optimization: Survey of methods and
  industrial applications, Surveys on Mathematics for Industry 11 (2005) 1--42.

\bibitem{c33}
G.~Eichfelder, Scalarizations for adaptively solving multi-objective
  optimization problems, Comput. Optim. Appl. 44 (2009) 249--273.
\newblock \href {https://doi.org/10.1007/s10589-007-9155-4}
  {\path{doi:10.1007/s10589-007-9155-4}}.

\bibitem{c34}
S.~Piyavskii, An algorithm for finding the absolute extremum of a function,
  Comput. Maths. Math. Phys. 12~(4) (1972) 57--67.

\bibitem{c35}
B.~Shubert, A sequential method seeking the global maximum of a function,
  {SIAM} Journal on Numerical Analysis 9~(3) (1972) 379--388.

\bibitem{c36}
V.~Gergel, K.~Barkalov, A.~Sysoyev, Globalizer: A novel supercomputer software
  system for solving time-consuming global optimization problems, Numerical
  Algebra, Control {\&} Optimization 8 (2018) 47--62.
\newblock \href {https://doi.org/10.3934/naco.2018003}
  {\path{doi:10.3934/naco.2018003}}.

\bibitem{c37}
L.~Breiman, A.~Cutler, A deterministic algorithm for global optimization,
  Mathematical Programming 58 (1993) 179--199.
\newblock \href {https://doi.org/10.1007/BF01581266}
  {\path{doi:10.1007/BF01581266}}.

\bibitem{c38}
A.~{\v Z}ilinskas, J.~{\v Z}ilinskas, Adaptation of a one-step worst-case
  optimal univariate algorithm of bi-objective {Lipschitz} optimization to
  multidimensional problems, Commun Nonlinear Sci Numer Simulat 21~(1-3) (2015)
  89--98.
\newblock \href {https://doi.org/10.1016/j.cnsns.2014.08.025}
  {\path{doi:10.1016/j.cnsns.2014.08.025}}.

\bibitem{c39}
S.~Bleuler, M.~Laumanns, L.~Thiele, E.~Zitzler, {PISA-A} platform and
  programming language independent interface for search algorithms,
  Evolutionary Multi-Criterion Optimization, {LNCS} 2632 (2003) 494--508.
\newblock \href {https://doi.org/10.1007/3-540-36970-8_35}
  {\path{doi:10.1007/3-540-36970-8_35}}.

\bibitem{c40}
M.~Gaviano, D.~Kvasov, D.~Lera, Y.~Sergeyev, Software for generation of classes
  of test functions with known local and global minima for global optimization,
  {ACM} Transactions on Mathematical Software 29~(4) (2003) 469--480.

\bibitem{c41}
D.~Balandin, M.~Kogan, Multi-objective generalized {H2} control for optimal
  protection from vibration, {UKACC} 12th International Conference on Control
  ({CONTROL}), Sheffield (2018) 205--210. \href
  {https://doi.org/10.1109/CONTROL.2018.8516721}
  {\path{doi:10.1109/CONTROL.2018.8516721}}.

\end{thebibliography}
